EuPPollNet: A European database of plant-pollinator networks

### 2024-05-20 Manuscript/EuPPollNet_Ms.qmd
edits

Although Europe contains a much larger number of flowering plants than pollinator species (~4 to 1 ratio), the observed number of pollinator species almost doubled the one of observed plant species. This seems a common feature of phytocentric plant-pollinator networks, which tend to overlook rare plant species and capture a higher proportion of pollinator species [REF].

Discuss this

The number of pollinator species almost doubled the number of plant species within the database. This is a common aspect in phytocentric networks [@jordano2016], where an observer records the different pollinators that land on the reproductive structures of plants, resulting in a higher number of pollinator species per plant.

Link with connectance now?

>>>>

Although Europe contains a much larger number of flowering plants than pollinator species (~4 to 1 ratio), the observed number of pollinator species almost doubled the one of plants in the database. This could be explained by the fact that all networks are phytocentric, resulting in sampling bias towards pollinator species [@jordano2016; @vizentin2018]. While animal-centred sampling is likely to increase the plant-pollinator species ratio [e.g., @encinas2023], the spatial scale and environmental context of the sampled communities will also influence their observed diversity, especially given the ability to move of pollinators and the sessile nature of plants. As expected [@jordano1987], we found that network connectance decreased exponentially with the number of species. The less connected networks were the Alpine ones as they were the ones with higher number of species.

#Task: Calcular residual connectance.

with more species had lower connectance .

Finish this paragraph with an idea of how sampling can bias our view and that is important to be aware of that when understanding plant-pollinator patterns
